\input{title.tex}

### 2022-05-20 docs/papers/01_manuscript/manuscript.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0
feat(results,-structures): new figure 1
feat(institution-context): appendix sec1
fix(appendix): appendix sort
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:
feat: pca analysi

\usepackage{amsmath,graphicx,array}
\usepackage{dcolumn,soul}%
\let\openbox\relax
\usepackage{amsthm}
\usepackage[figuresright]{rotating}%
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{listings}%
\usepackage{hyperref}
\makeatletter
\def\uns{\ifmmode\,\else$\,$\fi}%
\newtheorem{theorem}{Theorem}
\newtheorem{construction}{Construction}
\newtheorem{estimate}{Estimate}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{result}{Result}
\newtheorem{algth}{Algorithm}
\newtheorem{proposition}{Proposition}
\newtheorem{hypothesis}{Hypothesis}
\newtheorem{experiment}{Experiment}
\newtheorem{definition}{Definition}
\newtheorem{condition}{Condition}
\newtheorem{property}{Property}
\newtheorem{problem}{Problem}
\newtheorem{fact}{Fact}
\newtheorem{assumption}{Assumption}
\newtheorem{eexample}{Example}
\newtheorem{model}{Model}
%%
\makeatother

@@

\dhead{RESEARCH ARTICLE}
\subhead{EARTH SCIENCES}
\newtheorem{ass}{Assumption}   % My command. Assumptions.
\newtheorem{case}{Case}  % My command. Cases

@@

\author{Shuang Song$^{1,2}$}
\author{Huiyu Wen$^3$}
\author{*Shuai Wang$^{1,2}$}
\author{Xutong Wu$^{1,2}$}

\author{Graeme S. Cumming$^{4}$}
\author{Bojie Fu$^{1,2,5}$}

@@

\affil{$^2$Institute of Land Surface System and Sustainability,
     Faculty of Geographical Science,
     Beijing Normal University,
     Beijing 100875,
     P.R. China}

\affil{$^3$School of Finance,
     Renmin University of China,
     Beijing 100875,
     P.R. China}

\affil{$^4$ARC Centre of Excellence for Coral Reef Studies,
     James Cook University,
     Townsville 4811,
     QLD, Australia}

\affil{$^5$The research for this article was financed by....... The authors thank....... for insightful comments and ....... for expert research assistance. A supplementary online appendix is available with this article at the \em{National Science Review} website.}

@@

%% Put the bibliography here, most people will use BiBTeX in
%% which case the environment below should be replaced with
%% the \bibliography{} command.
\bibliography{../WAInstitution_YRB_2021}\label{bib}
\end{document}

>>>>

\usepackage{amsmath,graphicx,array}
\usepackage{dcolumn,soul}%
\let\openbox\relax
\usepackage{amsthm}
\usepackage[figuresright]{rotating}%
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{listings}%
\usepackage{hyperref}
% \usepackage[nofiglist,notablist]{endfloat}
\makeatletter
\def\uns{\ifmmode\,\else$\,$\fi}%
\newtheorem{defn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{ass}{Assumption}
\newtheorem{prop}{Proposition}
\newtheorem{fig}{Fig.}
\newtheorem{case}{Case}
\newtheorem{case_appendix}{Case}
\newtheorem{example}{Example}[section]
\renewcommand{\proofname}{\textbf{Proof}}
\newtheorem{property}{Property}
\newtheorem{remark}{Remark}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}

\usepackage{booktabs}
\usepackage{diagbox}
%%
\makeatother

@@

\dhead{RESEARCH ARTICLE}
\subhead{EARTH SCIENCES}

@@

\author{Shuang Song$^{1}$}
\author{Huiyu Wen$^2$}
\author{*Shuai Wang$^{1}$}
\author{Xutong Wu$^{1}$}

\author{Graeme S. Cumming$^{3}$}
\author{Bojie Fu$^{1,4}$}

@@

% \affil{$^2$Institute of Land Surface System and Sustainability,
%      Faculty of Geographical Science,
%      Beijing Normal University,
%      Beijing 100875,
%      P.R. China}

\affil{$^2$School of Finance,
     Renmin University of China,
     Beijing 100875,
     P.R. China}

\affil{$^3$ARC Centre of Excellence for Coral Reef Studies,
     James Cook University,
     Townsville 4811,
     QLD, Australia}

\affil{$^4$The research for this article was financed by....... The authors thank....... for insightful comments and ....... for expert research assistance. A supplementary online appendix is available with this article at the \em{National Science Review} website.}

@@

\section{S1: Contexts of institutional shifts}\label{secS1}
\input{../02_appendix/01_institution_context.tex}

\section{S2: Sensitivity analysis}\label{secS2}
\input{../02_appendix/02_method_details.tex}

\section{S2: Methods in details}\label{secS3}
\input{../02_appendix/03_results_appendix.tex}

\section{S3: Optimization model for water use}\label{secS4}
\input{../02_appendix/04_theoretical_model.tex}

\section{S4: Model extensions}\label{secS5}
\input{../02_appendix/05_model_extensions.tex}

%% Put the bibliography here, most people will use BiBTeX in
%% which case the environment below should be replaced with
%% the \bibliography{} command.
\bibliography{../mybib}
\label{bib}
\end{document}

### 2022-05-20 docs/papers/02_appendix/02_method_details.tex
feat: pca analysis
BREAKING CHANGE:

% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables. All variables used are listed in Table~\ref{tab:variables}.
% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.

% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption. We then used the test dataset to test the model-fitting effect.
% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).

\begin{table}[!h]
	\caption{Variables and their categories for water use predictions}
	\scriptsize
	\label{tab:variables}
	\begin{tabular}{lllll}
	\hline
	Economic sector &
	  Category &
	  Unit &
	  Description &
	  Variables \\ \hline
	Agriculture &
	  Irrigation Area &
	  thousand ha &
	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
	Industry &
	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
	  Billion Yuan &
	  Industrial GVA by industries &
	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
	 &
	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
	  \% &
	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
	Services &
	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
	  Billion Yuan &
	  GVA of service activities &
	  Services GVA \\ \hline
	Domestic &
	  Urban population &
	  Million Capita &
	  Population living in urban regions. &
	  Urban pop \\
	 &
	  Rural population &
	  Million Capita &
	  Population living in rural regions. &
	  Rural pop \\
	 &
	  Livestock population &
	  Billion KJ &
	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
	  Livestock \\ \hline
	\end{tabular}
\end{table}

\begin{figure}[!thb]
	\centering
	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
	\caption{
		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
	}
\label{fig:linear}
\end{figure}

>>>>

There are two approaches in validity testing of the DSC: (1) comparing the post- and pre- period reconstructions, (2) testing robustness through placebo analysis.

A good synthetic control will reconstruct (a) the outcome of the treated unit and (b) the covariates of the treated unit over the pre-treatment period. The plots and the Root Mean Square Percentage Error (RMSPE) help us evaluate (a), this table is meant to evaluate (b). If the synthetic control has good fit, the following things should be true:

Each row of the first two columns should be approximately equal. This means the synthetic control has reconstructed the treated unit values.

Placebo analysis is another standard approach to.

### 2022-05-20 docs/papers/02_appendix/03_results_appendix.tex
feat: pca analysis
BREAKING CHANGE:

The Differenced Synthetic Control (DSC) method estimates water use $y'$ by assuming that the control group (provinces out of the YRB) and experiment group (provinces in the YRB) keep their changing trends after an institutional shift in $t_0$, i.e., $f_{t<t_0}(X) = f_{t>t_0}(X)$.
Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$), there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
Corresponding to the problem of this study, they mean: (1) Institutional shift changes the trend of independent variables (environment, economy, technology); (2) Institutional shift makes difference of water use caused by the change of unit independent variable combination different.

@@

where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1975, 2008]$.

@@

>>>>

\subsection*{Sensitive analysis}

\subsection*{}

The Differenced Synthetic Control (DSC) method estimates water use $y'$ by assuming that the control group (provinces out of the YRB) and experiment group (provinces in the YRB) keep their changing trends after an institutional shift in $t_0$, i.e., $f_{t<t_0}(X) = f_{t>t_0}(X)$.
Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$, there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
Corresponding to the problem of this study, they mean: (1) Institutional shift changes the trend of independent variables (environment, economy, technology); (2) Institutional shift makes difference of water use caused by the change of unit independent variable combination different.

@@

where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1979, 2008]$.

@@

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
    \centering
    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}
    \label{fig:elbow}
\end{figure*}

### 2022-05-20 docs/papers/02_appendix/04_theoretical_model.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:
feat: pca analysis
BREAKING CHANGE:

In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional mismatch could have led to the sprint effect in water use, especially among provinces with high incentives for excess water use. Specifically, we modeled individual provincial decision-making in water resources before quota execution.

@@

Extensions of the model are shown in \textit{Appendix S5}.%%%

\begin{case_appendix}Centralized decision

>>>>

In order to understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic economic model to analyze how institutional mismatch could have led to the changes of water use, especially among provinces with high incentives for excess water use. Specifically, we modeled individual provincial decision-making in water resources before quota execution.

@@

Extensions of the model are shown in Supplementary Material S3.%%%

%Appendix的模型和proposition推导细节部分
%放在Appendix
Appendix: Water Use Optimization

%case1
\begin{case_appendix}Centralized decision
